ODGI: understanding pangenome graphs

### 2021-10-26 manuscript/main.tex
discussion: viz + scWGS

(recent) interactive visualization tools?! CITE PANACHE, also indicate that no published tool for interactive exploration of such graphs exist
\FIXME{mention gfaestus?}

is ODGI ready for scWGS data? potentially, each cell is a path in a graph!! very very high path depth

>>>>

ODGI's visualization tools produce static, large-scale snapshots. Recent interactive browsers are reference centric \citep{Beyer2019, Yokoyama2019, Durant2021} or focusing on one dimension \citep{Wick_2015}. However, an interactive visualization solution that combines the 1D and 2D layout of a graph with annotation and read mapping information across different zoom levels is still missing. ODGI's graph layout algorithms could become a backbone of such tools, as is already the case for \textit{gfaestus}\footnote{\url{https://github.com/chfi/gfaestus}}, which currently relies on the \textit{odgi layout} output for its interactive 2D visualization.

So far, ODGI has not been applied to graphs build from scWGS \citep{Zhuo2021} data. Each cell would be represented as a path in the graph, the path depth would be very high. As ODGI was designed to deal with the path depth of human pangenome graphs, it remains to be seen, if it will work equally well with scWGS data.
